---
title: "Test geocoding"
author: "Alan Jackson"
date: '2022-04-09'
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(data.table)
library(dtplyr)
library(microbenchmark)

Archive_path <- "/home/ajackson/Dropbox/Rprojects/Curated_Data_Files/CoH_Address_Points/"
df <- readRDS(paste0(Archive_path, "COH_Geocoding_Locations.rds"))
dt <- as.data.table(df)

filename <- "COH_PDD_ADDRESS_POINTS_-_PDD.csv"

dfraw <- read_csv(paste0(Archive_path, filename),
               col_types="nnccccccccccccccnnccccccccccccccc")

knitr::opts_chunk$set(echo = TRUE)
```

##  Try out some strategies

- match everything
- match close to name
- return several possibilities, ranked
- Test timing on tibble vs table

```{r create test data}

testdata <- tribble(
  ~Street_num, ~Prefix, ~Street_name, ~Street_type, ~Zipcode,
  "1311",      ""     , "TULANE"    , "ST"        , "77008"
)

testset <- readRDS("/home/ajackson/Dropbox/Rprojects/Curated_Data_Files/Houston_Permits/Permit_data.rds") %>% head(., n=500)

```

```{r test things}

mbm <- microbenchmark(
"a"={
  df[
  (df$Street_num==testdata$Street_num) &
  (df$Street_name==testdata$Street_name) &
  (df$Street_type==testdata$Street_type) &
  (df$Prefix==testdata$Prefix) &
  (df$Zipcode==testdata$Zipcode),] 
},

"b"={
  df %>% filter(Street_num==testdata$Street_num,
              Street_name==testdata$Street_name,
              Street_type==testdata$Street_type,
              Prefix==testdata$Prefix,
              Zipcode==testdata$Zipcode)
},

"c"={
  dt[Street_num==testdata$Street_num &
     Street_name==testdata$Street_name &
     Street_type==testdata$Street_type &
     Prefix==testdata$Prefix &
     Zipcode==testdata$Zipcode]
# },
# 
# "d"={
#   dti[Street_num==testdata$Street_num &
#      Street_name==testdata$Street_name &
#      Street_type==testdata$Street_type &
#      Prefix==testdata$Prefix &
#      Zipcode==testdata$Zipcode]
}
)

mbm

```

I think we have a winner. After looking at how to use indexed tables, I think
I will defer. Not using that seems fast enough.

## let's build a simple app to test

Create a bigger dataset, and build a simple function

```{r next}

#   First clean up input

library(postmastr)
pm_dictionary(type = "state", filter = c("TX"), case = "title", locale = "us")
dirs <- pm_dictionary(type = "directional", filter = c("N", "S", "E", "W"), locale = "us")
TX <- pm_dictionary(type = "state", filter = "TX", case = c("title", "upper"), locale = "us")
cities <- pm_append(type = "city",
                    input=c("HOUSTON", "WEST UNIVERSITY PL", "UNINCORPORATED",     
                            "TOMBALL", "PASADENA", "SOUTHSIDE PLACE", 
                            "HUMBLE", "BAYTOWN", "KATY", 
                            "JACINTO CITY", "DEER PARK", "LA PORTE", 
                            "WEBSTER", "CYPRESS", "JERSEY VILLAGE", 
                            "PINEY POINT VILLAGE", "NASSAU BAY", "MISSOURI CITY", 
                            "BELLAIRE", "SEABROOK", "SPRING VALLEY", 
                            "SHOREACRES", "GALENA PARK", "SOUTH HOUSTON", 
                            "PEARLAND", "HUNTERS CREEK", "HEDWIG VILLAGE", 
                            "BUNKER HILL", "TAYLOR VILLAGE", "MORGANS POINT", 
                            "EL LAGO", "HILSHIRE VILLAGE", "LEAGUE CITY", 
                            "SPRING", "FRIENDSWOOD", "WALLER", 
                            "RICHMOND", "ATASCOCITA", "STAFFORD", 
                            "KINGWOOD", "HUFFMAN", "CHANNELVIEW", 
                            "NEW CANEY", "NORTH BELT", "CLEAR BROOK CITY",
                            "BUNKER HILL VILLAGE", "CROSBY"),
                  output=c("HOUSTON", "WEST UNIVERSITY PL", "UNINCORPORATED",     
                            "TOMBALL", "PASADENA", "SOUTHSIDE PLACE", 
                            "HUMBLE", "BAYTOWN", "KATY", 
                            "JACINTO CITY", "DEER PARK", "LA PORTE", 
                            "WEBSTER", "CYPRESS", "JERSEY VILLAGE", 
                            "PINEY POINT VILLAGE", "NASSAU BAY", "MISSOURI CITY", 
                            "BELLAIRE", "SEABROOK", "SPRING VALLEY", 
                            "SHOREACRES", "GALENA PARK", "SOUTH HOUSTON", 
                            "PEARLAND", "HUNTERS CREEK", "HEDWIG VILLAGE", 
                            "BUNKER HILL", "TAYLOR VILLAGE", "MORGANS POINT", 
                            "EL LAGO", "HILSHIRE VILLAGE", "LEAGUE CITY", 
                            "SPRING", "FRIENDSWOOD", "WALLER", 
                            "RICHMOND", "ATASCOCITA", "STAFFORD", 
                            "KINGWOOD", "HUFFMAN", "CHANNELVIEW", 
                            "NEW CANEY", "NORTH BELT", "CLEAR BROOK CITY",
                            "BUNKER HILL VILLAGE", "CROSBY"))

foo <- testset %>% 
#   get rid of address like 325 1/2. Get rid of the fraction
  mutate(Address=str_replace(Address, "^(\\d+ )\\d/\\d ", "\\1")) %>% 
#   Protect farm roads by adding an "A" at end that will later go away
  mutate(Address=str_replace(Address, " F M ", " FM ")) %>% 
#   Remove BLD (Building) designator
  mutate(Address=str_replace(Address, " BLD ", " ")) %>% 
#   streets deignated are Private are special and hard to geocode.
#   We will remove that designation, but then flag it in a comments column
  mutate(Special=ifelse(str_detect(Address, " \\(PVT\\)"), "Private", "")) 


mask <- str_detect(foo$Address,"FM 1960|FM 2100|FM 2351|FM 529|FM 2920|FM 1485
|FM 2855|FM 1093|FM 2234|FM 362|FM 1942|FM 1314|FM 1463
|FM 723|FM 1464|FM 686|FM 2978|FM 528|FM 521
|FM 1098|FM 149|FM 1959|FM 359|FM 1488|FM 249
|FM 2917|FM 1736|FM 526" )

#   protect from removing ending numbers

foo[mask,]$Address <- paste(foo[mask,]$Address, "A") 

foo <- pm_identify(foo, var="Address") # add ID fields
foo2 <- pm_prep(foo, var="Address", type="street") # Prep data
#pm_postal_all(foo2) # do all have zip?
#foo2 <- pm_postal_parse(foo2)
foo2 <- pm_houseFrac_parse(foo2)
foo2 <- pm_house_parse(foo2)

#   Here we pause to remove room numbers and such
foo2 <- foo2 %>% 
  mutate(pm.address=str_remove(pm.address, " [A-Z] & [A-Z]$")) %>% 
  mutate(pm.address=str_remove(pm.address, " FL \\d+$")) %>% # ending numbers
  mutate(pm.address=str_remove(pm.address, " BLD \\d+$")) %>% # ending numbers
  mutate(pm.address=str_remove(pm.address, " \\d+$")) %>% # ending numbers
  #mutate(pm.address=str_remove(pm.address, " [A-Z]$")) %>% # ending single alpha
  mutate(pm.address=str_remove(pm.address, " BLD\\s*$")) %>% # ending BLD
  mutate(pm.address=str_remove(pm.address, " \\(PVT\\)")) %>%  # PVT
  mutate(pm.address=str_remove(pm.address, " BLD\\d+$")) %>% # ending BLD
  mutate(pm.address=str_remove(pm.address, " LVL\\d+$")) %>% # ending BLD
  mutate(pm.address=str_remove(pm.address, " ACRX$")) %>% # ending BLD
  mutate(pm.address=str_remove(pm.address, " CNPY[A-Z]*$")) %>% 
  mutate(pm.address=str_remove(pm.address, " BSMT$")) %>% 
  mutate(pm.address=str_remove(pm.address, " FL$")) %>% 
  mutate(pm.address=str_remove(pm.address, " B\\d-\\d$")) %>% 
  mutate(pm.address=str_remove(pm.address, " $\\d+[A-Z]+")) %>% 
  mutate(pm.address=str_remove(pm.address, "\\s*$")) %>% 
  mutate(pm.address=str_remove(pm.address, " GARG$")) %>% 
  mutate(pm.address=str_remove(pm.address, " XYZ$")) %>% 
  mutate(pm.address=str_replace(pm.address, " AVE .+$", " AVE"))# %>% 

#   streets deignated are Private are special and hard to geocode.
#   We will remove that designation, but then flag it in a comments column

foo2 <- foo2 %>% 
  mutate(Special=ifelse(str_detect(pm.address, " \\(PVT\\)"), "Private", "")) %>% 
  mutate(pm.address=str_remove(pm.address, " \\(PVT\\)")) # PVT


#   remove ending alphas but protect certain street names:
#   AVENUE, Z AND Z, T BAR M, O S T, LAZY J, H AND R, DIAMOND M

mask2 <- str_detect(
  foo2$pm.address,"AVENUE|Z AND Z|T BAR M|O S T|LAZY J|H AND R|DIAMOND M")

foo2[!mask2,]$pm.address <- str_remove(foo2[!mask2,]$pm.address," [A-DF-MO-RT-VX-Z]$")

foo2 <- pm_streetDir_parse(foo2, dirs)
foo2 <- pm_streetSuf_parse(foo2)
foo2 <- pm_street_parse(foo2)

foo2 <- foo2 %>% 
  mutate(pm.street=str_replace(pm.street, " 1 At 2", " 1/2")) 

foo2 <- foo2 %>% 
  mutate(pm.street=str_to_upper(pm.street)) %>% 
  mutate(pm.streetSuf=str_to_upper(pm.streetSuf)) %>% 
  mutate(pm.preDir=replace_na(pm.preDir, "")) %>% 
  mutate(pm.streetSuf=replace_na(pm.streetSuf, ""))

foo <- pm_replace(foo2, source=foo)

#unique((filter(df, str_detect(Street_name, "^FM ")))$Street_name)

#unique(df$Street_type)

```

##    Now do some geocoding

Need to be smart about this and allow for failure modes

Test for each field in succession so that a reasonable error message can be
emitted when things go south.

- zip
- street
- address
- street type
- prefix

```{r main event}

tmpout <- NULL
failout <- NULL
Audits <- NULL
for (i in 1:nrow(foo)) {
  print(foo[i,]$Address)
  audit <- tribble(~Address, ~Zip, ~Street_name, 
                   ~Street_type, ~Street_num, ~Prefix)
  audit[1,]$Address <- paste(foo[i,]$pm.house, foo[i,]$pm.preDir,
                             foo[i,]$pm.street, foo[i,]$pm.streetSuf,
                             foo[i,]$Zipcode) 
  tmp <- dt[Zipcode==foo[i,]$Zipcode]
  audit$Zip <- nrow(tmp) # how many addresses in zipcode found?
  if (nrow(tmp)==0){
    print("--zip")
    failout <- foo[i,] %>%
      mutate(Fail="Zipcode") %>% 
      rbind(failout)
    next()
  }
  
  tmp <- tmp[Street_name==foo[i,]$pm.street]
  audit$Street_name <- nrow(tmp) # how many names found?
  if (nrow(tmp)==0){
    print("--name")
    failout <- foo[i,] %>%
      mutate(Fail="Name") %>% 
      rbind(failout)
    next()
  }
  
  tmp <- tmp[Street_type==foo[i,]$pm.streetSuf]
  audit$Street_type <- nrow(tmp) # how many of street type found?
  if (nrow(tmp)==0){
    print("--type")
    failout <- foo[i,] %>%
      mutate(Fail="Type") %>% 
      rbind(failout)
    next()
  }
  
  tmp <- tmp[Street_num==foo[i,]$pm.house]
  audit$Street_num <- nrow(tmp) # how many of street number found?
  if (nrow(tmp)==0){
    print("--Number")
    failout <- foo[i,] %>%
      mutate(Fail="Number") %>% 
      rbind(failout)
    next()
  }
  
  tmp <- tmp[Prefix==foo[i,]$pm.preDir]
  audit$Prefix <- nrow(tmp) # How many of street prefix found?
  if (nrow(tmp)==0){
    print("--prefix")
    failout <- foo[i,] %>%
      mutate(Fail="Prefix") %>% 
      rbind(failout)
    next()
  }
  
  Audits <- rbind(Audits, audit)
  
#  if (nrow(tmp)==0) {
#    print("     ")
#    print("------  no hits")
#    print(foo[i,]$Address)
#    failout <- rbind(failout, foo[i,])
#  }
  
  if (nrow(tmp)>1) {
    print("     ")
    print(paste("------",nrow(tmp), "hits"))
    print(foo[i,]$Address)
    
  }
  
  tmpout <- rbind(tmpout, tmp)
}

#   Initialize success flag

failout <- failout %>% mutate(Success=FALSE)

```

##        Let's try some repair strategies

For names, look at lexical distance. What is a reasonable search radius? 2? 3?

For Street type, look at the set of allowed types for that street name in that zip.

for number, look for numbers +- 10 or so and interpolate if distance small

for prefix, look at allowed for street in zip. If ambiguous, then can't resolve



```{r repair name}
#     Lets make a dataset containing only Street_name, Street_type, Prefix, 
#     and Zip

df_names_only <- df %>% 
  group_by(Zipcode, Street_name, Street_type, Prefix) %>% 
    summarize(Zipcode=last(Zipcode),
              Street_name=last(Street_name),
              Street_type=last(Street_type),
              Prefix=last(Prefix),
              n=n()
              ) %>% 
  ungroup() %>% 
  filter(n>1) # I don't trust the singletons

####################
#Zip <- failout[45,]$Zipcode  
#Name <- failout[45,]$pm.street  
#Type <- failout[45,]$pm.streetSuf  
#prefix <- failout[45,]$pm.preDir  
  
####################
  
Repair_name <- function(df, Zip, Name, Type, prefix, distance=2) {
  #   Use a list of street names per zip as df
  #   Zip and Name are the input hopefully good zip and unmatched name
  #   Distance is lexical distance
  foo <- df %>% 
  #   Filter out streets where this will likely fail
    filter(str_length(Street_name)>3) %>% #  eliminate short names
    filter(!str_detect(Street_name, "STREET")) %>% # eliminate A STREET, B STREET
    filter(!str_detect(Street_name, "^\\d+TH")) %>% # eliminate 4TH, 5TH, etc
    filter(!str_detect(Street_name, "^CR \\d+")) %>%  # eliminate county roads
    filter(Zipcode==Zip,
           Street_type==Type,
           Prefix==prefix
           ) %>% 
    mutate(dist=adist(Street_name, Name)) %>% 
    filter(dist<=distance,
           dist > 0)
  
  foo$Street_name
}

eraseme <- NULL
foobar <- failout %>% filter(Fail=="Name")
for (i in 1:nrow(foobar)) {
  print(paste("Names",i, foobar[i,]$pm.street))
  foo <- Repair_name(df_names_only,
                     Zip=foobar[i,]$Zipcode,
                     Name=foobar[i,]$pm.street,
                     Type=foobar[i,]$pm.streetSuf,
                     prefix=foobar[i,]$pm.preDir,
                     distance=2
                     )
  print(paste("---",foo))
  if (!identical(foo,character(0))){ #  Flag success
    failout[failout$pm.id==foobar[i,]$pm.id,]$Success=TRUE
  }
  eraseme <- rbind(eraseme, foo)
}
```

##        Street types repairs

```{r repair type}

Repair_type <- function(df, Zip, Name, Type, prefix){
  #   What are the available type in the zip for that name?
  #   If only one, use it. If more than one, emit choices.
  #   unless it is CIR or CT
  #foo <- df_names_only %>% 
  foo <- df %>% 
    filter(Zipcode==Zip,
           Street_name==Name,
           Prefix==prefix
           )  
  print(paste(Name, foo$Street_type))
  if (nrow(foo)>0) {
    return(foo) # return the Street_type and number of hits
  } else {
    return(paste("What the hell just happened?", prefix, Name, Type, Zip))
  }
}

####################
# Zip <- failout[44,]$Zipcode  
# Name <- failout[44,]$pm.street  
# Type <- ""
# prefix <- failout[44,]$pm.preDir  
####################
  
eraseme <- NULL
foobar <- failout %>% filter(Fail=="Type")
for (i in 1:nrow(foobar)) {
  foo <- Repair_type(df_names_only,
                     Zip=foobar[i,]$Zipcode,
                     Name=foobar[i,]$pm.street,
                     Type=foobar[i,]$pm.streetSuf,
                     prefix=foobar[i,]$pm.preDir
                     )
  
  if (nrow(foo)==1){ #  Flag success
    failout[failout$pm.id==foobar[i,]$pm.id,]$Success=TRUE}
  eraseme <- rbind(eraseme, foo)
}
```

##        Repair prefix

Much like the street type. Look in zip and vote. If ambiguous, fail.

More ambitious, to be done later?, would be to check for similar address range
in the given zipcode to disambiguate the prefix.

```{r repair prefix}

Repair_prefix <- function(df, Zip, Name, Type, prefix){
  #   What are the available prefix in the zip for that name?
  #   If more than one, emit choices.
  #foo <- df_names_only %>% 
  foo <- df %>% 
    filter(Zipcode==Zip,
           Street_name==Name,
           Street_type==Type
           )  
  print(paste(foo$Prefix, Name))
  if (nrow(foo)>0) {
    return(foo) # return the Street_type and number of hits
  } else {
    return(paste("What the hell just happened?", prefix, Name, Type, Zip))
  }
}

####################
Zip <- failout[44,]$Zipcode  
Name <- failout[44,]$pm.street  
Type <- failout[44,]$pm.streetSuf  
prefix <- failout[44,]$pm.preDir  
#prefix <- ""
####################
  
eraseme <- NULL
foobar <- failout %>% filter(Fail=="Prefix")
for (i in 1:nrow(foobar)) {
  foo <- Repair_prefix(df_names_only,
                     Zip=foobar[i,]$Zipcode,
                     Name=foobar[i,]$pm.street,
                     Type=foobar[i,]$pm.streetSuf,
                     prefix=foobar[i,]$pm.preDir
                     )
  #print(paste(failout[i,4:7], foo))
  if (nrow(foo)==1){ #  Flag success
    failout[failout$pm.id==foobar[i,]$pm.id,]$Success=TRUE}
  eraseme <- rbind(eraseme, foo)
}
```

##        Repair the Address number

Basically need to somehow interpolate the numbers that are close.


```{r repair Number}

Repair_number <- function(df, Number, Zip, Name, Type, prefix, distance=10){
  #   What are the available prefix in the zip for that name?
  #   If more than one, emit choices.
  foo <- dt %>% 
    filter(Zipcode==Zip,
           Street_name==Name,
           Prefix==prefix,
           Street_type==Type
           ) %>% 
    as_tibble()
  
  Target <- as.numeric(Number) # set up for comparisons
  foo$Street_num <- as.numeric(foo$Street_num)
  
  #   Restrict to one block
  
  Target_min <- round(Target, -2)
  Target_max <- Target_min+99
  
  #   Restrict to same side of street
  Sample <- foo %>% 
    filter(between(Street_num, (Target_min), (Target_max))) %>% 
    filter(Street_num%%2 == Target%%2)  
  
  if (nrow(Sample)<2){ # hard to interpolate one value
    print("first try fail")
    #   open up to 3 blocks
  Target_min <- round(Target, -2)-100
  Target_max <- Target_min+199
  Sample <- foo %>% 
    filter(between(Street_num, (Target_min), (Target_max))) %>% 
    filter(Street_num%%2 == Target%%2)  
  }
  
  if (nrow(Sample)<2){ # If still too few, hang it up
    print("second try fail")
    return(tribble(~Address, ~Lon, ~Lat, Target, 0, 0)) 
  }
  
  #   Main event. Collaspe identical numbers,
  #   Calculate a delta lat/long scaled by delta address
  #   Then use the nearest address to apply that.
  
  Interpolator <- 
    Sample %>% 
    arrange(Street_num) %>% 
    group_by(Street_num) %>% 
      summarize(Street_num=last(Street_num),
                Lon=mean(Lon),
                Lat=mean(Lat)) %>% 
    mutate(Dx=Lon-lag(Lon),
           Dy=Lat-lag(Lat),
           Dnum=Street_num-lag(Street_num)) %>% 
    mutate(Dx=(Dx/Dnum),
           Dy=(Dy/Dnum))
  Interpolator[1,]$Dx <- Interpolator[2,]$Dx # replace NA
  Interpolator[1,]$Dy <- Interpolator[2,]$Dy # replace NA
  
 foo2 <- Interpolator[which.min(abs(Interpolator$Street_num-Target)),] 
  
 New_Lon <- foo2$Lon-(foo2$Street_num-Target)*foo2$Dx
 New_Lat <- foo2$Lat-(foo2$Street_num-Target)*foo2$Dy
 
# p <- 
# Sample %>% ggplot(aes(x=Lon, y=Lat)) +
#   geom_point() +
#   geom_point(data=Est_pt, aes(x=Lon, y=Lat), color="red")+
#   geom_label(data=Est_pt, aes(label=Address), color='red')+
#   geom_label(aes(label=Street_num))
 
 Est_pt <- tribble(~Address, ~Lon, ~Lat, 
                   Target, New_Lon, New_Lat) 
 
  return(Est_pt)
} #####    end of Repair_number  ##############

####################
Zip <- failout[1,]$Zipcode  
Name <- failout[1,]$pm.street  
Type <- failout[1,]$pm.streetSuf  
prefix <- failout[1,]$pm.preDir  
Number <- failout[1,]$pm.house  
#Number <- "911"
#prefix <- ""
####################
  
eraseme <- NULL
foobar <- failout %>% filter(Fail=="Number")
for (i in 1:nrow(foobar)) {
  print(paste(failout[i,]$pm.house,failout[i,]$pm.street, failout[i,]$Zipcode ))
  foo <- Repair_number(dt,
                     Number=foobar[i,]$pm.house,
                     Zip=foobar[i,]$Zipcode,
                     Name=foobar[i,]$pm.street,
                     Type=foobar[i,]$pm.streetSuf,
                     prefix=foobar[i,]$pm.preDir,
                     distance=10
                     )
  print(paste("--",i,"--"))
  #print(foo)
  if (foo$Lat>0){ #  Flag success
    failout[failout$pm.id==foobar[i,]$pm.id,]$Success=TRUE}
  eraseme <- rbind(eraseme, foo)
}

```

##        What is the zip is wrong?

For any left, do a final check to see if the zip is wrong.

If perfect match in another zip, and street name does not exist in given zip,
then we call it good.


```{r zip}

keepme <- failout
####################
Zip <- failout[17,]$Zipcode  
Name <- failout[17,]$pm.street  
Type <- failout[17,]$pm.streetSuf  
Prefix <- failout[17,]$pm.preDir  
Number <- failout[17,]$pm.house  
Zip <- "77001"
#prefix <- ""
####################


Repair_zip <- function(df, Zip, Name, Type, Prefix, Number){
  #   If a perfect match in another zip *and* the street does not exist
  #   in the given zip, then declare it fixed
  foo <- df %>% 
    filter(Street_num==Number,
           Street_name==Name,
           Prefix==Prefix,
           Street_type==Type
           ) %>% 
    as_tibble()
  
  print(paste("..1..",foo$Zipcode, Name))
  if (nrow(foo)==1) { # found just one hit
    #   Does that street exist in the given zip?
    foo2 <- df %>% 
      filter(Zipcode==Zip,
             Street_name==Name
             ) %>% 
      as_tibble()
  #print(paste("..2..",foo2$Zipcode))
      if (nrow(foo2)==0){ # looks good return new zip
        return(foo$Zipcode)
      }
  }
  return("None")
}

eraseme <- NULL
foobar <- failout %>% filter(!Success)
for (i in 1:nrow(foobar)) {
  print(paste(foobar[i,]$pm.house,foobar[i,]$pm.street, foobar[i,]$Zipcode ))
  foo <- Repair_zip(dt,
                     Number=foobar[i,]$pm.house,
                     Zip=foobar[i,]$Zipcode,
                     Name=foobar[i,]$pm.street,
                     Type=foobar[i,]$pm.streetSuf,
                     Prefix=foobar[i,]$pm.preDir
                     )
  print(paste("--",i,"--"))



  print(paste("---",foo))
  if (foo!="None"){ #  Flag success
    failout[failout$pm.id==foobar[i,]$pm.id,]$Success=TRUE
    print("Success")
  }
  eraseme <- rbind(eraseme, foo)
}

```

